Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
Fixed gitignore
newcommand for non-recognizable journals
Modified abstract

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

%\documentclass[useAMS,usenatbib]{mn2e}
\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

@@

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$University of California, Davis, Davis 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

@@

\begin{abstract}
With the latest infrared image of B1555+375, an edge-on disk is shown to over cross the strong lensed images. Indicating the flux ratio anomalie of B1555+375 is dominanted by its edge-on disk structure. We present a lens model with SIE bulge and exponential disk, base on the radio observation from \citet{Marlow}. And apply this model to SHARP infrared image.
\end{abstract}

\begin{keywords}
gravitaional lensing.
\end{keywords}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
\usepackage[nottoc]{tocbibind}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

% Journal definitions
\newcommand{\apj}[1]{ApJ}
\newcommand{\mnras}[1]{MNRAS}
\newcommand{\apjl}[1]{ApJL}
\newcommand{\pasj}[1]{PASJ}
\newcommand{\aj}[1]{AJ}
\newcommand{\nat}[1]{Nature}

@@

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

@@

\begin{abstract}

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  Several [??]
other lens systems that we have observed with adaptive optics imaging
as part of the Strong lensing at High Angular Resolution Programme (SHARP)
show similar behaviour.  These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

\end{abstract}

\begin{keywords}
gravitational lensing
\end{keywords}
